Seminarium TI 3700\\ Data Analysis on Twitter: An Overview

### 2014-03-26 paper_final.tex
usecase chapter volledig

\section*{Analysing a set of tweets}
What we have seen so far was the analysis on one tweet. This is all very interesting from a computer science point of view. All the different techniques to extract the meaning of a tweet in such a way that it is machine interpretable. However, the real knowledge is in the big data, not in a single tweet. Extracting that knowledge poses a whole new set of problems. In this part we will elaborate on User Classification, Tag Based analysis and Event Identification

@@

>>>>

\section*{Analysing a set of tweets}

Now that we understand how the data of tweets are enriched, and how their sentiment is deduced, we hold the building blocks to create techniques that are able
to analyse bigger sets of data. The analysis of a set of tweets is the key to creating applications based on Twitter information, of which some examples
will be introduced in the next chapter. There are three common techniques used within the field of social web data analytics, which are the User Classification,
the Tag Based Analysis and the Event Identification. The User Classification technique focussen on classifying every single tweet into a proposed set of classes.
The Tag Based Analysis tries to link users based on the content that they attach to their tweets. Content can be another user, a hashtag subject, an image, url, etc.
Event Identification has the goal of identifying real world events based upon a set of tweets.

@@

We have seen how researcher obtain tweets for data, and how useful information is extracted from them. This chapter focussen on the application of this information.
Given are two real world use cases that show why it is useful to extract information from the social web. The first use case illustrates the classification
of users in political views in order to make predictions about an outcome of an election. The second use case is about how Twitter can be used to detect
earthquakes by recognizing earthquake-related tweets that happen in real time.
